\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{fontspec}

% Set Calibri as the main font
\setmainfont{Calibri}

\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	linkcolor=black
}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\newcommand{\link}[1]{\href{#1}{LINK}}
\newcommand{\certificate}[1]{\href{#1}{CERTIFICATE}}

\newcommand{\resumesection}[1]{
	\vspace{0.2cm}
	\hrule
	\vspace{0.2cm}
	\centerline{\large\textbf{#1}}
	\vspace{0.15cm}
}

\begin{document}
	
	\pagenumbering{gobble}
	
	% Header with name, profiles, and contact info
	\noindent
	\begin{center}
		\textbf{\Huge SAI ABBHIRAM VALUPADASU} \\[0.3em]
		\href{mailto:valupadasusaiabbhiram@gmail.com}{valupadasusaiabbhiram@gmail.com} \,|\, 
		\href{https://www.linkedin.com/in/sai-abbhiram-valupadasu/}{LinkedIn} \,|\, 
		\href{https://github.com/ValupadasuSaiAbbhiram}{GitHub} \,|\, 
		\href{https://saiabbhiram-portfolio.vercel.app}{Portfolio} \,|\,
		\href{tel:+919849786297}{+91 9849786297}
	\end{center}
	
	
	\resumesection{PROFESSIONAL SUMMARY}
	\noindent
	Enthusiastic and detail-oriented Computer Science graduate with hands-on experience in \textbf{SOC operations, incident monitoring, and threat analysis}. Skilled in \textbf{log analysis, malware investigation, and triaging alerts}, with proficiency in security tools such as \textbf{Wireshark, Nmap, Snort, Splunk (basic)} and scripting in \textbf{Bash \& Python}. Strong foundation in networking, operating systems, and cloud security. Seeking a \textbf{SOC Analyst role} to contribute to proactive defense and incident response in a 24/7 environment.
	
	
	\resumesection{EDUCATION}
	\noindent \textbf{Vignana Bharathi Institute of Technology}\ \hfill Hyderabad
	\begin{itemize}
		\item B.Tech in Computer Science \& Engineering (Business Systems) | GPA: 7.8 \textbf{\hfill 2021 -- 2024}
	\end{itemize}
	
	\noindent \textbf{Central Institute of Tool Design} \hfill Hyderabad
	\begin{itemize}
		\item Diploma in Automation \& Robotics Engineering | GPA: 7.7 \textbf{\hfill 2019-2021}
	\end{itemize}
	
	
	\resumesection{SKILLS SUMMARY}
	\noindent \begin{tabularx}{\textwidth}{@{}lX@{}}
		\textbf{Security Tools:} & Wireshark, Nmap, Burp Suite, Snort, Splunk (basic), ELK Stack (basic), Kali Linux \\
		\textbf{Operating Systems:} & Windows, Linux, OS X \\
		\textbf{Scripting/Programming:} & Shell Scripting (Bash), Python, Java, SQL, C \\
		\textbf{Networking:} & TCP/IP, Firewalls, IDS/IPS, Packet Analysis, Log Monitoring \\
		\textbf{Soft Skills:} & Incident Triage, Threat Hunting, Team Collaboration, Communication \\
	\end{tabularx}
	
	
	\resumesection{RELEVANT EXPERIENCE \& LABS}
	\noindent \textbf{Cybersecurity Labs \& Blue Team Practice | TryHackMe, HackTheBox \hfill 2024 -- 2025} 
	\begin{itemize}
		\item Completed hands-on labs covering SOC fundamentals, alert triage, malware investigation, and log analysis.
		\item Performed network packet captures using Wireshark to detect brute force, phishing, and data exfiltration attempts.
		\item Conducted vulnerability scans with Nmap and implemented incident response steps following defined playbooks.
		\item Used Splunk queries for log searching, correlation, and initial triage of events.
	\end{itemize}
	
	\vspace{0.1cm}
	\noindent \textbf{Independent Projects \hfill 2023 -- Present} 
	\begin{itemize}
		\item Built monitoring dashboards and data analytics pipelines (Python, SQL) to strengthen anomaly detection skills.
		\item Developed automation scripts in Python and Bash for log parsing, alerting, and remediation.
		\item Designed and deployed applications on cloud (AWS, Docker) with security best practices for authentication and access control.
	\end{itemize}
	
	
	\resumesection{PROJECTS}
	\noindent \textbf{Network Security Monitoring Lab | Self-Project \hfill 2024}
	\begin{itemize}
		\item Configured Wireshark and Snort to capture and analyze suspicious traffic patterns from simulated attacks.
		\item Performed incident triage following SOC playbooks, escalating critical findings to simulated higher-tier analysts.
		\item Documented detailed root cause analysis reports with remediation strategies to mitigate vulnerabilities.
		\item Continuously tuned detection rules to improve monitoring accuracy and reduce false positives.
	\end{itemize}
	
	\vspace{0.1cm}
	\noindent \textbf{Cartlytics – Market Basket Analysis | \link{https://github.com/ValupadasuSaiabbhiram/Cartlytics} \hfill 2023}
	\begin{itemize}
		\item Applied data mining techniques to identify hidden patterns in datasets, showcasing analytical problem-solving.
		\item Built interactive Streamlit dashboard with support, confidence, and lift metrics to visualize insights.
		\item Drew parallels to SOC use cases by leveraging anomaly detection methods for identifying outliers in logs.
	\end{itemize}
	
	\vspace{0.1cm}
	\noindent \textbf{Threat Hunting Challenges | TryHackMe \hfill 2024}
	\begin{itemize}
		\item Investigated simulated phishing, brute force, and malware attacks using forensic log analysis.
		\item Followed structured triage and escalation workflows similar to SOC environments.
		\item Created post-incident reports detailing timeline, indicators of compromise (IOCs), and preventive measures.
	\end{itemize}
	
	
	\resumesection{CERTIFICATIONS}
	\noindent \textbf{Cyber Security 101 | TryHackMe} \hfill Feb 2025

	
	\noindent \textbf{Advent of Cyber | TryHackMe} \hfill Dec 2024

	
	\noindent \textbf{Networking Essentials | Cisco NetAcad} \hfill Oct 2022

	
	\noindent \textbf{AWS Academy Cloud Foundations | AWS} \hfill Dec 2022
	
\end{document}
