\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{fontspec}

% Set Calibri as the main font
\setmainfont{Calibri}

\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	linkcolor=black
}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

\newcommand{\link}[1]{\href{#1}{LINK}}

\newcommand{\certificate}[1]{\href{#1}{CERTIFICATE}}

\newcommand{\resumesection}[1]{
	\vspace{0.2cm}
	\hrule
	\vspace{0.2cm}
	\centerline{\large\textbf{#1}}
	\vspace{0.15cm}
}

\begin{document}
	
	\pagenumbering{gobble}
	
	% Header with name, profiles, and contact info
	\noindent
	\begin{center}
		\textbf{\Huge SAI ABBHIRAM VALUPADASU} \\[0.3em]
		\href{mailto:valupadasusaiabbhiram@gmail.com}{valupadasusaiabbhiram@gmail.com} \,|\, 
		\href{https://www.linkedin.com/in/sai-abbhiram-valupadasu/}{LinkedIn} \,|\, 
		\href{https://github.com/ValupadasuSaiAbbhiram}{GitHub} \,|\, 
		\href{https://saiabbhiram-portfolio.vercel.app}{Portfolio} \,|\,
		\href{tel:+919849786297}{+91 9849786297}
	\end{center}
	
	
	\resumesection{EDUCATION}
	
		\noindent \textbf{Vignana Bharathi Institute of Technology}\ \hfill Hyderabad
		\begin{itemize}
			\item B.Tech in Computer Science \& Engineering (Business Systems) | GPA: 7.8 \textbf{\hfill 2021 -- 2024}
		\end{itemize}
		
		\noindent \textbf{Central Institute of Tool Design} \hfill Hyderabad
		\begin{itemize}
			\item Diploma in Automation \& Robotics Engineering | GPA: 7.7 \textbf{\hfill 2019-2021}
		\end{itemize}
	
	\resumesection{SKILLS SUMMARY}
	\noindent \begin{tabularx}{\textwidth}{@{}lX@{}}
		\textbf{Programming:} & Python, Java, SQL, C \\
		\textbf{Salesforce:} & Apex, SOQL, Triggers, Lightning Web Components (LWC), Visualforce, Flows, Process Builder \\
		\textbf{Frameworks/Libraries:} & Pandas, Numpy, Scikit-Learn, Matplotlib \\
		\textbf{Databases:} & MySQL, MongoDB, SQLite \\
		\textbf{Tools \& Platforms:} & Power BI, Tableau, Excel, PyCharm, Jupyter Notebook, VS Code, IntelliJ IDEA, Docker, AWS \\
		\textbf{Soft Skills:} & Rapport Building, Stakeholder Management, Team Collaboration, Effective Communication \\
	\end{tabularx}

	\resumesection{EXPERIENCE}
	
	\noindent \textbf{INDEPENDENT SOFTWARE DEVELOPER | Hyderabad, India | \link{https://github.com/ValupadasuSaiAbbhiram} \hfill{May 2024 - Present}} 
	\begin{itemize}
		\item Designed and developed scalable applications integrating business logic, user experience, and modern frameworks (React.js, Node.js, Salesforce Platform).
		\item Delivered projects including \textit{Spotlight (Real-Time Social Network)} and \textit{Netflix-Clone}, demonstrating skills in full-stack development, database design, and authentication systems.
		\item Built and deployed cloud-ready solutions with Docker, MongoDB, and AWS services to ensure performance and scalability.
		\item Collaborated with Agile teams, applying Scrum methodologies to deliver maintainable and efficient solutions on time.
	\end{itemize}
	\vspace{0.1cm}
	\textbf{SALESFORCE VIRTUAL INTERNSHIP | SmartBridge | \link{https://www.salesforce.com/trailblazer/svalupadasu} \hfill{Oct 2023 -- Mar 2024}} 
	\begin{itemize}
		\item Customized Salesforce CRM by creating custom objects, workflows, and validation rules to streamline business processes.
		\item Developed Apex classes, triggers, and SOQL queries to automate data validation and reporting tasks.
		\item Built Lightning Web Components (LWC) for interactive dashboards and user-friendly UI enhancements.
		\item Integrated Salesforce tools (Flows, Process Builder) to optimize automation and improve operational efficiency.
	\end{itemize}
	
	
	\resumesection{PROJECTS}
	
	\noindent \textbf{Cartlytics – Market Basket Analysis | \link{https://github.com/ValupadasuSaiabbhiram/Cartlytics} \hfill{Aug 2023 -- Dec 2023}}
	\begin{itemize}
		\item Implemented the FP-Growth algorithm to identify purchasing patterns and associations from transaction datasets.
		\item Designed and deployed an interactive Streamlit dashboard with visualizations of support, confidence, lift, and conviction metrics.
		\item Enabled data-driven decision making by uncovering cross-selling opportunities and actionable business insights.
	\end{itemize}
	\vspace{0.1cm}
	\noindent \textbf{FashionX – Fashion Recommender System | \link{https://github.com/ValupadasuSaiAbbhiram/FashionX}\hfill{Jan 2024 - Apr 2024}} 
	\begin{itemize}
		\item Built a fashion recommender using ResNet50 and Nearest Neighbors to provide personalized product suggestions.
		\item Deployed as a Dockerized Streamlit application for seamless scalability and user accessibility.
		\item Enhanced user experience by integrating real-time recommendation updates with visual similarity search.
	\end{itemize}
	
	\resumesection{CERTIFICATES}
		\noindent \textbf{Salesforce Administrator Trailmix | \certificate{https://www.salesforce.com/trailblazer/svalupadasu} \hfill{Mar 2024}}
		\begin{itemize}
			\item Gained hands-on experience with Salesforce CRM including objects, workflows, validation rules, and automation tools.
			\item Learned Salesforce security, user management, and business process customization.
		\end{itemize}
		
		\noindent \textbf{Salesforce Developer Trailmix | \certificate{https://www.salesforce.com/trailblazer/svalupadasu} \hfill{Jan 2024}}
		\begin{itemize}
			\item Developed Apex classes, triggers, SOQL queries, and Lightning Web Components (LWC).
			\item Built and deployed end-to-end Salesforce customizations and automation workflows.
		\end{itemize}
		
		\noindent \textbf{AWS Academy Cloud Foundations | \certificate{https://github.com/ValupadasuSaiabbhiram/Certificates/blob/main/AWS_Academy_Graduate___AWS_Academy_Cloud_Foundations_Badge20230729-28-vxr2h0.pdf} \hfill{Dec 2022}} 
		\begin{itemize}
			\item Gained knowledge of core AWS services including EC2, S3, IAM, and VPC.
			\item Built understanding of cloud architecture, security, and deployment.
		\end{itemize}
	
	
\end{document}