\documentclass[10pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{pdfcomment}

% ---------- Formatting ----------
\pagestyle{empty}
\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\vspace{0.5pt}\titlerule]
\setlist[itemize]{leftmargin=1.5em,itemsep=0.2pt,topsep=0.2pt, parsep=0.2pt, topsep=2pt}


% ---------- Document ----------
\begin{document}
	
	% ===== Header =====
	\begin{center}
		
		{\LARGE \textbf{Sai Abbhiram Valupadasu}}\\[6pt]
		Hyderabad, India \,|\,
		\href{tel:+91 9849786297}{+91 9849786297} \,|\,
		\href{mailto:valupadasusaiabbhiram@gmail.com}{Gmail} \,|\,
		\href{https://www.linkedin.com/in/Sai-Abbhiram-Valupadasu}{LinkedIn} \,|\,
		\href{https://github.com/ValupadasuSaiabbhiram}{GitHub} \,|\,
		\href{https://personal-portfolio-tan-nine-78.vercel.app/}{Portfolio-Website}
		
	\end{center}
	
	% ===== Education =====
	\section*{Education}
	
	
	\textbf{B.Tech — Computer Science \& Engineering (Business Systems)} \hfill \textit{2021 -- 2024}\\
	Vignana Bharathi Institute of Technology \,\textbar \, Hyderabad \hfill CGPA: 7.8 
	\vspace{0.3em}  % adds vertical space 
	\\ \textbf{Relevant Coursework:} Data Structures \& Algorithms, DBMS, Software Engineering, \pdftooltip{ML}{Machine Learning}, \pdftooltip{AI}{Artificial Intelligence}, Web Development, Operating Systems, Computer Networks, Agile Development.
	
	
	% ===== Experience =====
	\section*{Experience}
	
	\textbf{Independent Software Developer}\, \textbar \, Self-Employed \,\textbar \, Hyderabad \hfill \textit{May 2024 -- Present}
	
	\begin{itemize}
		\item \textbf{Spotlight — Real-Time Social Network} \hfill \textit{May 2025 -- Present}
		\begin{itemize}
			\item Built a cross-platform app (iOS, Android, Web) with React Native + Expo.  
			\item Integrated Convex backend for real-time data sync with \textbf{under 200ms latency}.  
			\item Implemented Clerk authentication, reducing login failures by \textbf{25\%}.    
			\item \emph{Links:} \href{https://github.com/ValupadasuSaiabbhiram/SPOTLIGHT-APP}{GitHub}
		\end{itemize}
		
		\item \textbf{Netflix-Clone} \hfill \textit{Jan 2025 -- April 2025}
		\begin{itemize}
			\item Built a MERN-based streaming app with secure authentication and responsive media UI, achieving \textbf{95\% feature similarity} to Netflix core design.  
			\item Optimized backend APIs (Node.js/Express.js) with MongoDB, reducing query latency by \textbf{30\%}.  
			\item \emph{Links:} \href{https://github.com/ValupadasuSaiabbhiram/netflix-clone}{GitHub}
		\end{itemize}
			
	\end{itemize}
	

	% ===== Academic Projects =====
	\section*{Academic Projects}
	
	\textbf{FashionX \textbar \,Fashion Recommender System} \hfill \textit{Jan 2024 -- Apr 2024}
	\begin{itemize}
		\item Deep learning based fashion knowledge extraction using social media. Designed a recommender system Using ResNet50 for feature extraction, achieving \textbf{92\% accuracy} in similarity matching.  
		\item Applied Nearest Neighbors (scikit-learn) for fast retrieval, cutting response time by \textbf{40\%}.  
		\item Deployed a Dockerized Streamlit app, improving deployment efficiency by \textbf{60\%}.  
		\emph{Tech:} Python, TensorFlow/Keras, scikit-learn, NumPy, OpenCV, PIL, Streamlit, Docker.   
		\emph{Links:} \href{https://github.com/ValupadasuSaiabbhiram/FashionX}{GitHub}
	\end{itemize}
	
	\textbf{Cartlytics \textbar \,Market Basket Analysis (FP-Growth)} \hfill \textit{Aug 2023 -- Dec 2023}
	\begin{itemize}
		\item Built an interactive Streamlit app enabling CSV uploads and dynamic threshold tuning, reducing analysis time by \textbf{50\%}.  
		\item Implemented FP-Growth (mlxtend) to uncover frequent itemsets and association rules, improving recommendation insights by \textbf{35\%}.  
		\item Visualized results with Plotly/Matplotlib/PyVis, enhancing interpretability for users by \textbf{70\%}.  
		\emph{Tech:} Python, Streamlit, Pandas, NumPy, scikit-learn, Mlxtend, Plotly, PyVis, Matplotlib.  
		\emph{Links:} \href{https://github.com/ValupadasuSaiabbhiram/Cartlytics}{GitHub}
	\end{itemize}
	
	% ===== Technical Skills =====
	\section*{Technical Skills}
	
	\begin{itemize}[leftmargin=*]
 
	\item \textbf{Programming Languages:} Python, Java, C, SQL, JavaScript.
	\item \textbf{Web Development:} React.js, Next.js, Node.js, Express.js, HTML, CSS, Tailwind CSS, Headless UI.
	\item \textbf{Mobile Development:} React Native, Expo.
	\item \textbf{Databases/BaaS:} MongoDB, MySQL, Convex.
	\item \textbf{AI \& ML:} TensorFlow, Keras, scikit-learn, Pandas, NumPy, NLP (NLTK, spaCy), Recommendation Systems.
	\item \textbf{AI/LLM Tools:} Ollama, Hugging Face Transformers.
	\item \textbf{Tools \& Platforms:} Git, GitHub, Linux, VS Code, Postman, Clerk, Nodemailer, Cheerio, Cron Jobs.
	\item \textbf{Methodologies:} Asgile Scrum, Object-Oriented Design, REST API Development.
	\end{itemize}
	

	% ---------- Certifications ----------
	\section*{Certifications \hfill \small\href{https://github.com/ValupadasuSaiabbhiram/Certificates}{view all}}
	
	\begin{tabular}{p{0.33\linewidth} p{0.63\linewidth}}
		\textbullet\ \textbf{Angular}\, \textbar \, Infosys Springboard & \textbullet\ \textbf{Machine Learning, NLP \& Python}\, \textbar \, Infosys Springboard \\
		\textbullet\ \textbf{Database Foundations}\, \textbar \, Oracle  & \textbullet\ \textbf{The Complete Web Developer Course 2.0}\, \textbar \, Infosys Springboard \\
		\textbullet\ \textbf{AWS Cloud Foundations}\, \textbar \, AWS & \textbullet\ \textbf{Cyber Security 101}\, \textbar \, TryHackMe \\
		\textbullet\ \textbf{AWS ML Foundations}\, \textbar \, AWS & \textbullet\ \textbf{NDG Linux Unhatched}\, \textbar \, Cisco NetAcad\\
	\end{tabular}
	
	
	
	
\end{document}
